\documentclass[10pt]{article}
\usepackage{enumitem}
\usepackage{geometry}
\geometry{top=1in, bottom=1in, left=.5in, right=.5in}
\geometry{paperwidth=8.5in, paperheight=11in}
\setlength{\parindent}{0pt}
\begin{document}
\textbf{Education}\\[-2ex]
\rule{\textwidth}{0.4pt}\\ 
\vspace{-\baselineskip}
\begin{itemize}[itemsep=0pt, topsep=0pt]
\item GPA 3.92, anticipated B.A. with double major in Computer Science and Philosophy
\item Teaching Assistant for introductory and upper-level CS courses over five semesters
\item Activities include PAC Comedy Club, Opinions Columnist for the Williams Record Newspaper, WSO (student run website for Williams College)
\end{itemize}
\textbf{Projects}\\[-2ex]
\rule{\textwidth}{0.4pt}\\ 
\vspace{-\baselineskip}
\begin{itemize}[itemsep=0pt, topsep=0pt]
\item ML Lung Cancer Prediction Tool: Created a neural network to predict lung cancer based on several easily self-diagnosable conditions. Published a website where users can interact with this model to democratize access and allow users to play with the model.
\item Booktrak: Independently designed and created Booktrak for WSO (student run website for Williams College). Booktrak is a platform where Williams students can buy and sell used books, and link their book listings to specific classes in order to better facilitate used book sales. View Booktrak demo here.
\item GPT-Crossword: Used the ChatGPT API to create an AI powered crossword solving assistant which can give you hints or answers to your toughest crossword clues.
\item Devitas: Created Devitas — a free, easy-to-use website builder for students applying to college, jobs, and internships. Independently implemented full-stack web application using Node.js, JavaScript, and HTML.
\end{itemize}
\textbf{Research}\\[-2ex]
\rule{\textwidth}{0.4pt}\\ 
\vspace{-\baselineskip}
\begin{itemize}[itemsep=0pt, topsep=0pt]
\item Williams, Aaron. "Low Viral Load: Randomized Puzzles in Dr. Mario (1990-2001)."
\end{itemize}
\textbf{Languages \& Technologies}\\[-2ex]
\rule{\textwidth}{0.4pt}\\ 
\vspace{-\baselineskip}
\begin{itemize}[itemsep=0pt, topsep=0pt]
\item Javascript/Typescript, Python, HTML + CSS, F\#, Java, C, Go, Solidity, Assembly
\item React, Scikit-Learn, PyTorch, SolidJS, REST APIs, Next.js, Tailwind, GraphQL, Express.js, Firebase, MongoDB Atlas, AWS, Relay, Web3
\end{itemize}
\end{document}
